Dependently Typed Languages in Statix

### 2023-03-15 pres-evcs/presentation.tex
Add support for types to compiler
Work on presentation

@@

>>>>

\begin{frame}[fragile]{Type Checking}
	\begin{block}{Type checking relation}
		\texttt{typeOfExpr : scope * Expr -> Expr}
	\end{block}
	% Returns an Expr, not a Type
	% Scope -> Two different types of nodes
	\begin{block}{How do we use scopes?}
		One relation \texttt{name $\rightarrow$ NameEntry}, NameEntry is either:
		\begin{itemize}
			\item NType: Stores a type
			\item NSubst: Stores a substitution
		\end{itemize}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Requires Evaluation}
	\begin{exampleblock}{Example 1}
		\texttt{let T = Bool;\\let b: T = true;}
	\end{exampleblock}
	\begin{block}{Evaluation relation} 
		\texttt{betaHeadReduce : scope * Expr -> scope * Expr} \\
		\texttt{betaReduce : scope * Expr -> Expr} \\
		\texttt{exectBetaEq : (scope * Expr) * (scope * Expr)}
	\end{block}
\end{frame}

\begin{frame}[fragile]{Type Checking: Rules}
	\begin{figure}
		\centering
		\includegraphics[width=0.5\linewidth]{img/screenshot001}
		\label{fig:screenshot001}
	\end{figure}
	\begin{figure}
		\centering
		\includegraphics[width=0.5\linewidth]{img/screenshot002}
		\label{fig:screenshot002}
	\end{figure}

@@

\begin{frame}[fragile]{Conclusions}
	Spoofax is a great tool for developing dependently typed languages!\footnote{But there is still room for improvement}
\end{frame}
